### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/06_table_9_size_output.tex
back up before new paper

\begin{document}% Date and time: Sat, Apr 04, 2020 - 13:38:24
\begin{table}[!htbp] \centering 
  \caption{Deciles Employement} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.897$^{*}$ & $-$0.442$^{*}$ & $-$0.524$^{**}$ & $-$0.533$^{***}$ & $-$0.472$^{***}$ & $-$0.454$^{***}$ & $-$0.417$^{***}$ & $-$0.380$^{**}$ & $-$0.386$^{**}$ & $-$0.377$^{**}$ \\ 
  & (0.497) & (0.254) & (0.209) & (0.191) & (0.182) & (0.162) & (0.156) & (0.155) & (0.153) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  & 4.633$^{*}$ & 2.815$^{**}$ & 2.105$^{**}$ & 2.336$^{**}$ & 2.024$^{**}$ & 1.847$^{**}$ & 1.764$^{***}$ & 1.512$^{**}$ & 1.553$^{***}$ & 1.532$^{**}$ \\ 
  & (2.435) & (1.385) & (0.998) & (0.919) & (0.832) & (0.734) & (0.668) & (0.650) & (0.601) & (0.598) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:38:08
\begin{table}[!htbp] \centering 
  \caption{Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.348 & $-$0.127 & $-$0.280 & $-$0.201 & $-$0.228 & $-$0.252$^{*}$ & $-$0.227$^{*}$ & $-$0.210 & $-$0.221$^{*}$ & $-$0.213 \\ 
  & (0.357) & (0.183) & (0.177) & (0.163) & (0.156) & (0.145) & (0.136) & (0.135) & (0.134) & (0.135) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{ci}  & 2.118$^{*}$ & 0.628 & 0.535 & 0.148 & 0.482 & 0.608 & 0.546 & 0.478 & 0.541 & 0.529 \\ 
  & (1.118) & (0.798) & (0.500) & (0.572) & (0.488) & (0.427) & (0.394) & (0.383) & (0.373) & (0.374) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/07_table_9_size_capital.tex
back up before new paper

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:38:08
\begin{table}[!htbp] \centering 
  \caption{Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.348 & $-$0.127 & $-$0.280 & $-$0.201 & $-$0.228 & $-$0.252$^{*}$ & $-$0.227$^{*}$ & $-$0.210 & $-$0.221$^{*}$ & $-$0.213 \\ 
  & (0.357) & (0.183) & (0.177) & (0.163) & (0.156) & (0.145) & (0.136) & (0.135) & (0.134) & (0.135) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{ci}  & 2.118$^{*}$ & 0.628 & 0.535 & 0.148 & 0.482 & 0.608 & 0.546 & 0.478 & 0.541 & 0.529 \\ 
  & (1.118) & (0.798) & (0.500) & (0.572) & (0.488) & (0.427) & (0.394) & (0.383) & (0.373) & (0.374) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:38:57
\begin{table}[!htbp] \centering 
  \caption{Deciles Capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.445 & $-$0.200 & $-$0.322$^{*}$ & $-$0.232 & $-$0.260 & $-$0.281$^{*}$ & $-$0.251$^{*}$ & $-$0.234$^{*}$ & $-$0.244$^{*}$ & $-$0.235$^{*}$ \\ 
  & (0.350) & (0.186) & (0.179) & (0.166) & (0.161) & (0.148) & (0.137) & (0.137) & (0.136) & (0.137) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{ci}  & 2.065$^{**}$ & 0.852 & 0.562 & 0.240 & 0.479 & 0.560 & 0.499 & 0.445 & 0.499 & 0.485 \\ 
  & (0.922) & (0.638) & (0.469) & (0.467) & (0.411) & (0.366) & (0.337) & (0.332) & (0.323) & (0.324) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.861 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/08_table_9_size_employement.tex
back up before new paper

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:38:57
\begin{table}[!htbp] \centering 
  \caption{Deciles Capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.445 & $-$0.200 & $-$0.322$^{*}$ & $-$0.232 & $-$0.260 & $-$0.281$^{*}$ & $-$0.251$^{*}$ & $-$0.234$^{*}$ & $-$0.244$^{*}$ & $-$0.235$^{*}$ \\ 
  & (0.350) & (0.186) & (0.179) & (0.166) & (0.161) & (0.148) & (0.137) & (0.137) & (0.136) & (0.137) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{ci}  & 2.065$^{**}$ & 0.852 & 0.562 & 0.240 & 0.479 & 0.560 & 0.499 & 0.445 & 0.499 & 0.485 \\ 
  & (0.922) & (0.638) & (0.469) & (0.467) & (0.411) & (0.366) & (0.337) & (0.332) & (0.323) & (0.324) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.861 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:40:08
\begin{table}[!htbp] \centering 
  \caption{Deciles Employement} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.420 & $-$0.159 & $-$0.272 & $-$0.191 & $-$0.218 & $-$0.257$^{*}$ & $-$0.232$^{*}$ & $-$0.213 & $-$0.225$^{*}$ & $-$0.215 \\ 
  & (0.371) & (0.192) & (0.173) & (0.167) & (0.161) & (0.148) & (0.137) & (0.136) & (0.135) & (0.136) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{ci}  & 2.038$^{*}$ & 0.640 & 0.343 & 0.039 & 0.300 & 0.477 & 0.432 & 0.369 & 0.431 & 0.415 \\ 
  & (1.112) & (0.796) & (0.486) & (0.530) & (0.466) & (0.407) & (0.373) & (0.365) & (0.355) & (0.355) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.861 & 0.854 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/09_decile_6.tex
back up before new paper

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 09:34:53
\begin{table}[!htbp] \centering 
  \caption{Baseline regression} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.147 & 0.147 & 0.147 & $-$0.060 & $-$0.061 & $-$0.061 \\ 
  & (0.160) & (0.159) & (0.159) & (0.114) & (0.113) & (0.112) \\ 
  capital_{cit} & 1.468$^{**}$ & 1.468$^{**}$ & 1.468$^{**}$ & 0.945$^{**}$ & 0.946$^{**}$ & 0.949$^{**}$ \\ 
  & (0.723) & (0.727) & (0.722) & (0.474) & (0.474) & (0.471) \\ 
  labour_{cit} & 2.993$^{***}$ & 2.991$^{***}$ & 2.990$^{***}$ & 1.513 & 1.499 & 1.495 \\ 
  & (0.821) & (0.819) & (0.822) & (1.006) & (1.010) & (1.002) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.121 & $-$0.131 & $-$0.124 & $-$0.213 & $-$0.235$^{*}$ & $-$0.215 \\ 
  & (0.110) & (0.116) & (0.114) & (0.135) & (0.137) & (0.136) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{ci}  & $-$0.093 &  &  & 0.529 &  &  \\ 
  & (0.327) &  &  & (0.374) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{ci}  &  & $-$0.008 &  &  & 0.485 &  \\ 
  &  & (0.282) &  &  & (0.324) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{ci}  &  &  & $-$0.059 &  &  & 0.415 \\ 
  &  &  & (0.307) &  &  & (0.355) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.347 & 0.347 & 0.347 & 0.851 & 0.852 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 09:42:44
\begin{table}[!htbp] \centering 
  \caption{Decile 6} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.145 & 0.145 & 0.145 & $-$0.061 & $-$0.062 & $-$0.062 \\ 
  & (0.159) & (0.159) & (0.159) & (0.113) & (0.112) & (0.112) \\ 
  capital_{cit} & 1.457$^{**}$ & 1.458$^{**}$ & 1.457$^{**}$ & 0.939$^{**}$ & 0.938$^{**}$ & 0.943$^{**}$ \\ 
  & (0.725) & (0.729) & (0.724) & (0.471) & (0.471) & (0.468) \\ 
  labour_{cit} & 3.043$^{***}$ & 3.042$^{***}$ & 3.046$^{***}$ & 1.548 & 1.545 & 1.536 \\ 
  & (0.809) & (0.808) & (0.809) & (0.980) & (0.976) & (0.973) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} & $-$0.155 & $-$0.170 & $-$0.159 & $-$0.228$^{*}$ & $-$0.249$^{*}$ & $-$0.229$^{*}$ \\ 
  & (0.109) & (0.115) & (0.113) & (0.132) & (0.134) & (0.133) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{output share SOE}_{ci}  & $-$0.079 &  &  & 0.393 &  &  \\ 
  & (0.334) &  &  & (0.382) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{capital share SOE}_{ci}  &  & 0.022 &  &  & 0.372 &  \\ 
  &  & (0.284) &  &  & (0.329) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{labour share SOE}_{ci}  &  &  & $-$0.040 &  &  & 0.290 \\ 
  &  &  & (0.312) &  &  & (0.363) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.347 & 0.347 & 0.347 & 0.851 & 0.852 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/10_decile_7.tex
back up before new paper

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 09:42:44
\begin{table}[!htbp] \centering 
  \caption{Decile 6} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.145 & 0.145 & 0.145 & $-$0.061 & $-$0.062 & $-$0.062 \\ 
  & (0.159) & (0.159) & (0.159) & (0.113) & (0.112) & (0.112) \\ 
  capital_{cit} & 1.457$^{**}$ & 1.458$^{**}$ & 1.457$^{**}$ & 0.939$^{**}$ & 0.938$^{**}$ & 0.943$^{**}$ \\ 
  & (0.725) & (0.729) & (0.724) & (0.471) & (0.471) & (0.468) \\ 
  labour_{cit} & 3.043$^{***}$ & 3.042$^{***}$ & 3.046$^{***}$ & 1.548 & 1.545 & 1.536 \\ 
  & (0.809) & (0.808) & (0.809) & (0.980) & (0.976) & (0.973) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} & $-$0.155 & $-$0.170 & $-$0.159 & $-$0.228$^{*}$ & $-$0.249$^{*}$ & $-$0.229$^{*}$ \\ 
  & (0.109) & (0.115) & (0.113) & (0.132) & (0.134) & (0.133) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{output share SOE}_{ci}  & $-$0.079 &  &  & 0.393 &  &  \\ 
  & (0.334) &  &  & (0.382) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{capital share SOE}_{ci}  &  & 0.022 &  &  & 0.372 &  \\ 
  &  & (0.284) &  &  & (0.329) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{labour share SOE}_{ci}  &  &  & $-$0.040 &  &  & 0.290 \\ 
  &  &  & (0.312) &  &  & (0.363) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.347 & 0.347 & 0.347 & 0.851 & 0.852 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 09:43:17
\begin{table}[!htbp] \centering 
  \caption{Decile 7} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.147 & 0.147 & 0.147 & $-$0.060 & $-$0.061 & $-$0.061 \\ 
  & (0.160) & (0.159) & (0.159) & (0.114) & (0.113) & (0.112) \\ 
  capital_{cit} & 1.468$^{**}$ & 1.468$^{**}$ & 1.468$^{**}$ & 0.945$^{**}$ & 0.946$^{**}$ & 0.949$^{**}$ \\ 
  & (0.723) & (0.727) & (0.722) & (0.474) & (0.474) & (0.471) \\ 
  labour_{cit} & 2.993$^{***}$ & 2.991$^{***}$ & 2.990$^{***}$ & 1.513 & 1.499 & 1.495 \\ 
  & (0.821) & (0.819) & (0.822) & (1.006) & (1.010) & (1.002) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} & $-$0.121 & $-$0.131 & $-$0.124 & $-$0.213 & $-$0.235$^{*}$ & $-$0.215 \\ 
  & (0.110) & (0.116) & (0.114) & (0.135) & (0.137) & (0.136) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{output share SOE}_{ci}  & $-$0.093 &  &  & 0.529 &  &  \\ 
  & (0.327) &  &  & (0.374) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{capital share SOE}_{ci}  &  & $-$0.008 &  &  & 0.485 &  \\ 
  &  & (0.282) &  &  & (0.324) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{labour share SOE}_{ci}  &  &  & $-$0.059 &  &  & 0.415 \\ 
  &  &  & (0.307) &  &  & (0.355) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.347 & 0.347 & 0.347 & 0.851 & 0.852 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}
